An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-02-25 EconGrowth.Rnw
Now including code that correctly handles constraints on alpha, beta, and gamma for CD with energy fits. This new code also creates graphs of variation of SE, lambda, alpha, (and therefore beta) for a grid search over gamma.

@@

@@

      # gamma is a free parameter that we want to estimate

@@

      # We don't want to estimat the value of gamma

@@

@@

###############################
# Does a grid search over values of gamma for a CD production function
##
cdGrid <- function(countryAbbrev, energyType, gammaGrid){
  gamma <- c(0.1, 0.2)
  gamma <- gammaGrid
  models <- lapply(gamma, cobbDouglasModel, energyType=energyType, countryAbbrev=countryAbbrev)
  return(models)
}

seFromNlsModel <- function(model) { 
  return(summary(model)$sigma)
}

gammaGrid <- seq(0.05, 0.95, by=0.1)
models <- cdGrid("US", "Q", gammaGrid)
SSE <- lapply(models, function(model) summary(model)$sigma)
data <- cbind(gammaGrid, SSE)
print("US")
plot(gammaGrid, SSE)
print(coef(models[[2]]))

models <- cdGrid("ZA", "Q", gammaGrid)
SSE <- lapply(models, function(model) summary(model)$sigma)
data <- cbind(gammaGrid, SSE)
print("ZA")
plot(gammaGrid, SSE)
print(coef(models[[5]]))

# Some code that is helping to debug the Cobb-Douglas models. Randy Pruim is helping on this.

# print("cobbDouglasModel(US, Q) works fine:")
# us <- cobbDouglasModel("US", "Q")
# print(summary(us))
# print(confint(us))

# print("cobbDouglasModel(ZA) works fine")
# za <- cobbDouglasModel("ZA")
# print(summary(za))
# print(confint(za))

# print("cobbDouglasModel(ZA, Q) stops before convergence achieved,")
# print("and confint gives NA values:")
# za <- cobbDouglasModel("ZA", "Q")
# print(summary(za))
# print(confint(za))
# 
# print("cobbDouglasModel(UK, Q) also stops before convergence achieved,")
# print("but confint does not produce NA values:")
# uk <- cobbDouglasModel("UK", "Q")
# print(summary(uk))
# print(confint(uk))

>>>>

      gammaGuess <- 0.65 # Found via grid search over gamma

@@

      betaGuess <- 1.0 - alphaGuess - gammaGuess

@@

      # gamma is a free parameter. We need to estimate lambda, a, and b.

@@

      # We don't want to estimate the value of gamma

@@

                      algorithm = "port",
                      lower = list(lambda=-Inf, alpha=0),
                      upper = list(lambda=Inf, alpha=1.0-gamma)

@@

###############################
# Does a grid search over values of gamma for a CD production function
##
cdGrid <- function(countryAbbrev, energyType, gammaGrid){
  gamma <- gammaGrid
  models <- lapply(gamma, cobbDouglasModel, energyType=energyType, countryAbbrev=countryAbbrev)
  return(models)
}

gammaGrid <- seq(0.0, 0.95, by=0.05)
# print("US")
# models <- cdGrid("US", "Q", gammaGrid)
# SSE <- lapply(models, function(model) summary(model)$sigma)
# data <- cbind(gammaGrid, SSE)
# plot(gammaGrid, SSE)
# print(coef(models[[2]]))
# 
print("ZA")
models <- cdGrid("ZA", "Q", gammaGrid)
SSE <- lapply(models, function(model) summary(model)$sigma)
lambda <- lapply(models, function(model) coef(model)["lambda"])
alpha <- lapply(models, function(model) coef(model)["alpha"])
data <- cbind(lambda, alpha, gammaGrid, SSE)
print(data)
plot(gammaGrid, SSE)
plot(gammaGrid, lambda)
plot(gammaGrid, alpha)

# Some code to debug the Cobb-Douglas models. Randy Pruim is helping on this.

# print("cobbDouglasModel(US, Q) works fine:")
# us <- cobbDouglasModel("US", "Q")
# print(summary(us))
# print(confint(us))
# 
# print("cobbDouglasModel(ZA) works fine")
# za <- cobbDouglasModel("ZA")
# print(summary(za))
# print(confint(za))
# 
# print("cobbDouglasModel(ZA, Q) stops before convergence achieved,")
# print("and confint gives NA values:")
# za <- cobbDouglasModel("ZA", "Q")
# print(summary(za))
# print(confint(za))
# 
# print("cobbDouglasModel(UK, Q) also stops before convergence achieved,")
# print("but confint does not produce NA values:")
# uk <- cobbDouglasModel("UK", "Q")
# print(summary(uk))
# print(confint(uk))
